### 2016-09-30 results.tex
gbf

\begin{figure}[t]
\centering
\hfpagess{.45}{.45}
{
\adversaryv{$A_{\mathrm{ss}}^{\TestOracle,H}(\pubaux)$}\\[1ex]
$M \gets \pubaux$\\
for $\ell=1$ to $\binom{m}{k}$\\
\nudge $i_1,i_2,\ldots,i_k \gets \mathcal{I}_\ell$\\
\nudge $x \gets M[i_1] \xor M[i_2] \xor \cdots \xor M[i_k]$\\
\nudge if  $x \not\in S \wedge \left(\bigwedge_{j=1}^k H(j,x)=i_j \right)$ then \\
\nudge\nudge $a\gets\TestOracle(x)$\\
\nudge\nudge Return $\bot$\\
}
{
\adversaryv{$A_{\mathrm{ow}}^{H}(\pubaux)$}\\[1ex]
$M \gets \pubaux$\\
for $x \in X_1,X_2,\ldots,X_q$\\
\nudge for $j=1$ to $k$ \\
\nudge \nudge \nudge $i_j \gets H(j,x)$\\
\nudge $x' \gets M[i_1] \xor M[i_2] \xor \cdots \xor M[i_k]$\\
\nudge if $x' = x$ then Return $x$\\
Return~$X_{q+1}$
}
%{
%\adversaryv{$A^{\TestOracle}(\pubaux)$}\\[1ex]
%$M \gets \pubaux$\\
%for $1 \leq i_1 < i_2 < \cdots < i_k \leq m$\\
%\nudge $x \gets M[i_1] \xor M[i_2] \xor \cdots \xor M[i_k]$\\
%\nudge if $\TestOracle(x)=1$ then Return $\bot$
%}
%\caption{Adversary for Theorem~\ref{thm:xxx}.  \textbf{Left:} public hash case, \textbf{Right:} private hash case.}
\caption{{\bf Left:} Correctness attack for garbled Bloom filters with public~$M$.  The sequence $\mathcal{I}_1,\mathcal{I}_2,\ldots$ is some implicit enumeration of~$k$-tuples of indices over $[m]$.
{\bf Right:} One-wayness attack for garbled Bloom filters with public~$M$.  The sequence $X_1,X_2,\ldots,X_q,X_{q+1}$ are the $q+1$ most probable points in the support of~$\distr{}{}$ in decreasing order.  }
\label{fig:adv-gbf}
\end{figure}
Dong, Chen and Wen~\cite{xxx} introduce a set-membership data
structure called a \emph{garbled Bloom filter} (GBF).   Modulo some implementation
details, a GBF is like a classical Bloom filter, but
rather than storing a bit 1 at the indices determined by $H_j(x)$, the
GBF stores xor-shares of~$x$.  Thus, if $x \in S$, then hashing~$x$
and xoring together the strings stored at the indicated positions
recovers~$x$. We give the pseudocode for the GBF $\Rep$ and $\Qry$
algorithms in Figure~\ref{fig:gbf}.

@@

\heading{Privacy. }
We observe immediately that when~$\pubaux=\langle M \rangle$ the GBF cannot be SS-private (in the ROM) because $\privaux=\emptystring$.  In fact, the correctness attack given above suggests a one-wayness attack in the ROM, too; see the right half of Figure~\ref{fig:adv-gbf}.   The naive attack would simply output the most probable element in the support of the distribution $\distr{}{}$ used in the one-wayness experiment to sample~$S$.  But when~$M$ and the hash functions are available to the attacker, it can carry out set-membership tests for itself.  Thus the adversary on the right of Figure~\ref{fig:adv-gbf} tries the~$q$ most probable points, in order, halting with its output as soon as the set-membership test is successful.  If none of these points are yield a successful test, then the next most probable point is output.  The probabilty that $A_{ow}$ fails to win the one-wayness experiment is 
\begin{eqnarray*}
\AdvPrivOW{\setprim_{\mathrm{gbf}},\distr{}{}}{A_{\mathrm{ow}}} &= 1 - \Prob{X_1 \not\in S \wedge X_2 \not\in S \wedge \cdots \wedge X_{q+1}\not\in S} \\
& = 1 - \prod_{i=1}^{q+1} \Prob{X_i \not\in S \,|\, X_{i-1} \not\in S \wedge \cdots X_1 \not\in S}\Prob{X_1 \not\in S}\\
\end{eqnarray*}

 Thus the efficacy of the attack depends on the false positive rate. \todo{Either work out a proof for this case, or punt and make the attack more formal.}

>>>>

\begin{figure}[t]
\centering
\hfpagess{.45}{.45}
{
\adversaryv{$A_{\mathrm{ss}}^{\TestOracle,H}(\pubaux)$}\\[1ex]
$M \gets \pubaux$\\
for $\ell=1$ to $\binom{m}{k}$\\
\nudge $i_1,i_2,\ldots,i_k \gets \mathcal{I}_\ell$\\
\nudge $x \gets M[i_1] \xor M[i_2] \xor \cdots \xor M[i_k]$\\
\nudge if  $x \not\in S \wedge \left(\bigwedge_{j=1}^k H(j,x)=i_j \right)$ then \\
\nudge\nudge $a\gets\TestOracle(x)$\\
\nudge\nudge Return $\bot$\\
}
{
\adversaryv{$A_{\mathrm{ow}}^{H}(\pubaux)$}\\[1ex]
$M \gets \pubaux$\\
for $x \in X_1,X_2,\ldots,X_{q-1}$\\
\nudge for $j=1$ to $k$ \\
\nudge \nudge \nudge $i_j \gets H(j,x)$\\
\nudge $x' \gets M[i_1] \xor M[i_2] \xor \cdots \xor M[i_k]$\\
\nudge if $x' = x$ then Return $x$\\
Return~$X_{q}$
}
%{
%\adversaryv{$A^{\TestOracle}(\pubaux)$}\\[1ex]
%$M \gets \pubaux$\\
%for $1 \leq i_1 < i_2 < \cdots < i_k \leq m$\\
%\nudge $x \gets M[i_1] \xor M[i_2] \xor \cdots \xor M[i_k]$\\
%\nudge if $\TestOracle(x)=1$ then Return $\bot$
%}
%\caption{Adversary for Theorem~\ref{thm:xxx}.  \textbf{Left:} public hash case, \textbf{Right:} private hash case.}
\caption{{\bf Left:} Correctness attack for garbled Bloom filters with public~$M$.  The sequence $\mathcal{I}_1,\mathcal{I}_2,\ldots$ is some implicit enumeration of~$k$-tuples of indices over $[m]$.
{\bf Right:} One-wayness attack for garbled Bloom filters with public~$M$.  The sequence $X_1,X_2,\ldots,X_q,$ are the~$q$ most probable points in the support of~$\distr{}{}$ in decreasing order.  }
\label{fig:adv-gbf}
\end{figure}
Dong, Chen and Wen~\cite{xxx} introduce a set-membership data
structure called a \emph{garbled Bloom filter} (GBF).   Modulo some implementation
details, a GBF is like a classical Bloom filter, but
rather than storing a bit 1 at the indices determined by $H_j(x)$, the
GBF stores xor-shares of~$x$.  Thus, if $x \in S$, then hashing~$x$
and xoring together the strings stored at the indicated positions
recovers~$x$. We give the pseudocode for the GBF $\Rep$ and $\Qry$
algorithms in Figure~\ref{fig:gbf}.

@@

\heading{Privacy. }
We observe immediately that when~$\pubaux=\langle M \rangle$ the GBF cannot be SS-private (in the ROM) because $\privaux=\emptystring$.  In fact, the correctness attack given above suggests a one-wayness attack in the ROM, too; see the right half of Figure~\ref{fig:adv-gbf}.   The naive attack would simply output the most probable element in the support of the distribution $\distr{}{}$ used in the one-wayness experiment to sample~$S$.  But when~$M$ and the hash functions are available to the attacker, it can carry out set-membership tests for itself.  Thus the adversary on the right of Figure~\ref{fig:adv-gbf} tries the~$q-1$ most probable points, in order, halting with its output as soon as the set-membership test is successful.  If none of these points are yield a successful test, then the next most probable point is output.  It is not hard to conclude the following theorem.

\begin{theorem}
Fix $k,m,n,r,\lambda>0$, and let $\setprim_{\mathrm{gbf}}=(\Rep, \Qry)$ be the public~$M$ garbled Bloom filter, in the random-oracle model for~$H$.  Then 
\[
\AdvPrivOW{\setprim_{\mathrm{gbf}},\distr{}{}}{A_{\mathrm{ow}}} \geq 1 - (1-1/2^{\mu})^{q}
\]
 where $\mu = H_\infty(\distr{}{})$ is the pointwise min-entropy of~$\distr{}{}$, and $A_{\mathrm{ow}}$ makes $kq$ random-oracle queries.
\end{theorem}
%\begin{eqnarray*}
%\AdvPrivOW{\setprim_{\mathrm{gbf}},\distr{}{}}{A_{\mathrm{ow}}} &=& 1 - \Prob{X_1 \not\in S \wedge X_2 \not\in S \wedge \cdots \wedge X_{q+1}\not\in S} \\
%&=& 1 - \prod_{i=1}^{q+1} \Prob{X_i \not\in S \,|\, X_{i-1} \not\in S \wedge \cdots X_1 \not\in S}\Prob{X_1 \not\in S}\\
%\end{eqnarray*}
